|

### 2021-08-10 02-Chp-Systematic-Review-Tools.Rmd
End of day:

The package was been onboarded into the rOpenSci suite of packages, a collection of "carefully vetted, staff- and community-contributed R software tools that lower barriers to working with scientific data sources on the web".[@boettiger2015] As part of this process, following rigorous peer-review, an associated article introducing the tool was published by the Journal of Open Source Software.[@mcguinness2020a] The entire review discussion is publicly available and can be viewed online. [^chp-systematic-review-tools-4] The tool has also been well received by the open-source community, demonstrated by the engagement of other developers in contributing to important new functionality and suggesting bug-fixes.

[^chp-systematic-review-tools-4]: <https://github.com/ropensci/software-review/issues/380>

@@

>>>>

The package was been onboarded into the rOpenSci suite of packages, a collection of "carefully vetted, staff- and community-contributed R software tools that lower barriers to working with scientific data sources on the web".[@boettiger2015] As part of this process, following rigorous peer-review, an associated article introducing the tool was published by the Journal of Open Source Software.[@mcguinness2020a] The entire review discussion is publicly available and can be viewed online.[@zotero-15016] The tool has also been well received by the open-source community, demonstrated by the engagement of other developers in contributing to important new functionality and suggesting bug-fixes.

@@

### Use case

In addition to being used to search systematically search health-related preprint servers, as illustrated in the systematic review presented in Chapter \@ref(sys-rev-heading), `medrxivr` has other uses. For example, I led a descriptive analysis of the change data availability statements between preprinted and published versions of the same manuscript, stratified by journal data sharing policy access, underpinned by preprint meta-data provided by `medrixvr`.

We found <!-- TODO complete -->

This study has since been published in PLOS One, and a copy is included in Appendix \@ref() .
